Climatic warming strengthens a positive feedback\\ between alpine shrubs and fire \\[1cm] \huge Supplementary Material

### 2017-01-03 manuscript/supplementary.Rnw
Fixed figure references
Remove DOI, issue and volume placemarkers

% Please give the surname of the lead author for the running footer
\leadauthor{Camac} 
\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: james.camac@gmail.com}
\dates{This manuscript was compiled on \today}
\doi{\url{doi:10.1111/GCB.XXXXX}}

\begin{document}
\suppmaketitle
\tableofcontents
\clearpage
\listoffigures
\clearpage
\section{Study site}
Our research sites were on the Bogong High Plains, a series of alpine and high subalpine plateaux in the Alpine National Park, approximately 250 km northeast of Melbourne, Australia. The undulating terrain ranges in altitude from 1400 to 2000 m a.s.l and contains a well-developed mantle of soil. The most widespread soil type is ``alpine humus soil'', a friable, organic loam up to 1 m deep \citep{Williams:2014ud}. Mean annual temperature is approximately 6\textdegree C, with persistent snow cover from June to September. Annual precipitation is 1200 mm, yet droughts occur at roughly decadal intervals \citep{Wahren:2013ji}. The vegetation is a mosaic of Eucalypt-woodland and treeless vegetation, with the latter largely consisting of heathlands and tussock grasslands, but also herbfields and wetlands. The treeline is irregular (due to cold air drainage), occurring at altitudes ranging from 1600 to 1700 m a.s.l. Approximately 50\% of the alpine ‘treeless’ landscape consists of heathlands, most of which were extensively burned by a 400,000 ha wildfire in 2003 \citep[Fig. \ref{figS1};][]{Williams:2006tl,Camac:2013eb}. Large wildfires in Australian alpine landscapes have occurred once or twice per century and typically occur during periods of extended regional drought coupled with severe fire weather and multiple ignitions in the surrounding montane forests \citep{Williams:2008ba}.

@@

To simulate near-term warmer conditions indicated by the IPCC \citep{IPCC:2013vv}, we used Open Top Chambers (OTCs; Fig. \ref{figS2}) \citep{Molau:1996vc}. OTCs were hexagonal, 58 cm tall with an open-top diameter of 110 cm and base diameter of 168 cm. The chambers were constructed following the International Tundra Experiment (ITEX) protocols \citep{Molau:1996vc} using sun-lite: a lightweight shatter-resistant fiberglass with high light transmittance (86\%) and low infrared transmittance (\textless 5\%; Solar Components Corporation, USA).

@@

The study used 40 open heathland sites \citep[Fig. \ref{figS9};][]{Camac:2013eb} established immediately after the 2003 fires \citep{Williams:2006tl}. All sites have been free of grazing by cattle since 2003. Thirty sites were burnt, while the remaining ten were unburnt, likely for more than 70 years \citep{Camac:2013eb}. This disparity in sampling effort between burnt and unburnt was due to very few open heathland remaining unburnt after both the 2003 and 2007 fires. These sites encompassed most of the Bogong High Plains (120 km$^2$) and ranged in altitude from \Sexpr{round(min(complete_field_survey_data$altitude_m))} to \Sexpr{round(max(complete_field_survey_data$altitude_m))} m a.s.l. Sites were at least 0.25 ha and more than 500 m apart. In the summer of 2011-12, 9-years post-fire, seedling density in each site was estimated using forty 1 m$^2$ quadrats, evenly distributed in groups of 10 along four 50 m transects. Transects were positioned in the center of each site and were parallel to each other with exactly 10 m between transect lines. This effectively created a grid of 40 plots (10 plots by 4 transects) per site, subsampling an area of 2000 m$^2$.

>>>>

% Please give the surname of the lead author for the running footer
\leadauthor{Camac} 
\correspondingauthor{To whom correspondence should be addressed. E-mail: james.camac@gmail.com}
%\dates{This manuscript was compiled on \today}
%\doi{\url{doi:10.1111/GCB.XXXXX}}

\begin{document}
\suppmaketitle
\tableofcontents
\clearpage
\listoffigures
\clearpage
\section{Study site}
Our research sites were on the Bogong High Plains, a series of alpine and high subalpine plateaux in the Alpine National Park, approximately 250 km northeast of Melbourne, Australia. The undulating terrain ranges in altitude from 1400 to 2000 m a.s.l and contains a well-developed mantle of soil. The most widespread soil type is ``alpine humus soil'', a friable, organic loam up to 1 m deep \citep{Williams:2014ud}. Mean annual temperature is approximately 6\textdegree C, with persistent snow cover from June to September. Annual precipitation is 1200 mm, yet droughts occur at roughly decadal intervals \citep{Wahren:2013ji}. The vegetation is a mosaic of Eucalypt-woodland and treeless vegetation, with the latter largely consisting of heathlands and tussock grasslands, but also herbfields and wetlands. The treeline is irregular (due to cold air drainage), occurring at altitudes ranging from 1600 to 1700 m a.s.l. Approximately 50\% of the alpine ‘treeless’ landscape consists of heathlands, most of which were extensively burned by a 400,000 ha wildfire in 2003 \citep[Fig. \ref{figs1};][]{Williams:2006tl,Camac:2013eb}. Large wildfires in Australian alpine landscapes have occurred once or twice per century and typically occur during periods of extended regional drought coupled with severe fire weather and multiple ignitions in the surrounding montane forests \citep{Williams:2008ba}.

@@

To simulate near-term warmer conditions indicated by the IPCC \citep{IPCC:2013vv}, we used Open Top Chambers (OTCs; Fig. \ref{figs2}) \citep{Molau:1996vc}. OTCs were hexagonal, 58 cm tall with an open-top diameter of 110 cm and base diameter of 168 cm. The chambers were constructed following the International Tundra Experiment (ITEX) protocols \citep{Molau:1996vc} using sun-lite: a lightweight shatter-resistant fiberglass with high light transmittance (86\%) and low infrared transmittance (\textless 5\%; Solar Components Corporation, USA).

@@

The study used 40 open heathland sites \citep[Fig. \ref{figs9};][]{Camac:2013eb} established immediately after the 2003 fires \citep{Williams:2006tl}. All sites have been free of grazing by cattle since 2003. Thirty sites were burnt, while the remaining ten were unburnt, likely for more than 70 years \citep{Camac:2013eb}. This disparity in sampling effort between burnt and unburnt was due to very few open heathland remaining unburnt after both the 2003 and 2007 fires. These sites encompassed most of the Bogong High Plains (120 km$^2$) and ranged in altitude from \Sexpr{round(min(complete_field_survey_data$altitude_m))} to \Sexpr{round(max(complete_field_survey_data$altitude_m))} m a.s.l. Sites were at least 0.25 ha and more than 500 m apart. In the summer of 2011-12, 9-years post-fire, seedling density in each site was estimated using forty 1 m$^2$ quadrats, evenly distributed in groups of 10 along four 50 m transects. Transects were positioned in the center of each site and were parallel to each other with exactly 10 m between transect lines. This effectively created a grid of 40 plots (10 plots by 4 transects) per site, subsampling an area of 2000 m$^2$.
